# Colours

Here are some colours that I often use in R plots or in LaTeX documents. For each color, I provide the hexadecimal value and the RGB values. For some palettes, I gave names to the colors, so I provide some definitions in R and in LaTeX.

For LaTeX, the following package needs to be loaded to define our own colors:
```{latex, eval=FALSE}
\usepackage[dvipsnames]{xcolor}
```


Cool stuff for colour picking: <https://davidmathlogic.com/colorblind/>

```{r, echo=FALSE}
#1+1
```

```{css, echo=FALSE}
.sourceCode.r, div.sourceCode {
  background-color: initial;
  color: initial;
}
```


## Colours that are ok for color blindness and for printers


### Palette 1

```{css, echo=FALSE}
.color-light-blue {
  background-color: #a6cee3;
}
.color-dark-blue {
  background-color: #1f78b4;
}
.color-light-green {
  background-color: #b2df8a;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-light-blue
#| classes: color-light-blue
#| 
#a6cee3
```

```{markdown, eval=FALSE}
#| class-source: color-light-blue
#| classes: color-light-blue
#| 
rgb(166, 206, 227)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-dark-blue
#| classes: color-dark-blue
#1f78b4
```
```{markdown, eval=FALSE}
#| class-source: color-dark-blue
#| classes: color-dark-blue
rgb(31, 120, 180)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-light-green
#| classes: color-light-green
#b2df8a
```
```{markdown, eval=FALSE}
#| class-source: color-light-green
#| classes: color-light-green
rgb(178, 223, 138)
```
:::

::::


### Palette 2

```{css, echo=FALSE}
.color-deep-green {
  background-color: #1b9e77;
}
.color-orange {
  background-color: #d95f02;
}
.color-violet {
  background-color: #7570b3;
}
```

:::: {.columns}
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-deep-green
#| classes: color-deep-green
#| 
#1b9e77
```
```{markdown, eval=FALSE}
#| class-source: color-deep-green
#| classes: color-deep-green
#| 
rgb(27, 158, 119)
```
:::
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-orange
#| classes: color-orange
#d95f02
```
```{markdown, eval=FALSE}
#| class-source: color-orange
#| classes: color-orange
rgb(217, 95, 2)
```
:::
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-violet
#| classes: color-violet
#7570b3
```
```{markdown, eval=FALSE}
#| class-source: color-violet
#| classes: color-violet
rgb(117, 112, 179)
```
:::
::::



### Palette 3

```{css, echo=FALSE}

.color-cold-green {
  background-color: #66c2a5;
}
.color-tuile {
  background-color: #fc8d62;
}
.color-cold-violet {
  background-color: #8da0cb;
}
```

:::: {.columns}
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-cold-green
#| classes: color-cold-green
#| 
#66c2a5
```
```{markdown, eval=FALSE}
#| class-source: color-cold-green
#| classes: color-cold-green
#| 
rgb(102, 194, 165)
```
:::
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-tuile
#| classes: color-tuile
#fc8d62
```
```{markdown, eval=FALSE}
#| class-source: color-tuile
#| classes: color-tuile
rgb(252, 141, 98)
```
:::
::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-cold-violet
#| classes: color-cold-violet
#8da0cb
```
```{markdown, eval=FALSE}
#| class-source: color-cold-violet
#| classes: color-cold-violet
rgb(141, 160, 203)
```
:::
::::


## Color blind friendly

### Palette 1

```{css, echo=FALSE}
.color-rose {
  background-color: #D81B60;
}
.color-bleu {
  background-color: #1E88E5;
}
.color-cold-jaune {
  background-color: #FFC107;
}
.color-vert {
  background-color: #004D40;
}
```

:::: {.columns}
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-rose
#| classes: color-rose
#| 
#D81B60
```
```{markdown, eval=FALSE}
#| class-source: color-rose
#| classes: color-rose
#| 
rgb(216, 27, 96)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-bleu
#| classes: color-bleu
#1E88E5
```
```{markdown, eval=FALSE}
#| class-source: color-bleu
#| classes: color-bleu
rgb(30, 136, 229)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-jaune
#| classes: color-cold-jaune
#FFC107
```
```{markdown, eval=FALSE}
#| class-source: color-jaune
#| classes: color-cold-jaune
rgb(255, 193, 7)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-vert
#| classes: color-vert
#004D40
```
```{markdown, eval=FALSE}
#| class-source: color-vert
#| classes: color-vert
rgb(0, 77, 64)
```
:::
::::


### Palette 2 (Wong)

From @wong_2011_Nature.

```{css, echo=FALSE}
.color-wong-black {
  background-color: #000000;
}
.color-wong-gold {
  background-color: #E69F00;
}
.color-wong-light-blue {
  background-color: #56B4E9;
}
.color-wong-green {
  background-color: #009E73;
}
.color-wong-yellow {
  background-color: #F0E442;
}
.color-wong-blue {
  background-color: #0072B2;
}
.color-wong-orange {
  background-color: #D55E00;
}
.color-wong-purple {
  background-color: #CC79A7;
}
```


:::: {.columns}
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-black
#| classes: color-wong-black
#| 
#000000
```
```{markdown, eval=FALSE}
#| class-source: color-wong-black
#| classes: color-wong-black
#| 
rgb(0, 0, 0)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-gold
#| classes: color-wong-gold
#E69F00
```
```{markdown, eval=FALSE}
#| class-source: color-wong-gold
#| classes: color-wong-gold
rgb(230, 159, 0)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-light-blue
#| classes: color-wong-light-blue
#56B4E9
```
```{markdown, eval=FALSE}
#| class-source: color-wong-light-blue
#| classes: color-wong-light-blue
rgb(86, 180, 233)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-green
#| classes: color-wong-green
#009E73
```
```{markdown, eval=FALSE}
#| class-source: color-wong-green
#| classes: color-wong-green
rgb(0, 158, 115)
```
:::
::::

:::: {.columns}
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-yellow
#| classes: color-wong-yellow
#| 
#000000
```
```{markdown, eval=FALSE}
#| class-source: color-wong-yellow
#| classes: color-wong-yellow
#| 
rgb(240, 228, 66)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-blue
#| classes: color-wong-blue
#0072B2
```
```{markdown, eval=FALSE}
#| class-source: color-wong-blue
#| classes: color-wong-blue
rgb(0, 114, 178)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-orange
#| classes: color-wong-orange
#D55E00
```
```{markdown, eval=FALSE}
#| class-source: color-wong-orange
#| classes: color-wong-orange
rgb(213, 94, 0)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-wong-purple
#| classes: color-wong-purple
#CC79A7
```
```{markdown, eval=FALSE}
#| class-source: color-wong-purple
#| classes: color-wong-purple
rgb(204, 121, 167)
```
:::
::::


```{r}
wongBlack     <- "#000000"
wongGold      <- "#E69F00"
wongLightBlue <- "#56B4E9"
wongGreen     <- "#009E73"
wongYellow    <- "#F0E442"
wongBlue      <- "#0072B2"
wongOrange    <- "#D55E00"
wongPurple    <- "#CC79A7"
```

```{tex, eval=FALSE}
\definecolor{wongBlack}{RGB}{0,0,0}
\definecolor{wongGold}{RGB}{230, 159, 0}
\definecolor{wongLightBlue}{RGB}{86, 180, 233}
\definecolor{wongGreen}{RGB}{0, 158, 115}
\definecolor{wongYellow}{RGB}{240, 228, 66}
\definecolor{wongBlue}{RGB}{0, 114, 178}
\definecolor{wongOrange}{RGB}{213, 94, 0}
\definecolor{wongPurple}{RGB}{204, 121, 167}
```



### Palette 3 (IBM)

(The grey is an addition...)

```{css, echo=FALSE}
.color-IBM-blue {
  background-color: #648FFF;
}
.color-IBM-purple {
  background-color: #785EF0;
}
.color-IBM-magenta {
  background-color: #DC267F;
}
.color-IBM-orange {
  background-color: #FE6100;
}
.color-IBM-yellow {
  background-color: #FFB000;
}
.color-gris {
  background-color: #949698;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-IBM-blue
#| classes: color-IBM-blue
#| 
#648FFF
```

```{markdown, eval=FALSE}
#| class-source: color-IBM-blue
#| classes: color-IBM-blue
#| 
rgb(100, 143, 255)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-IBM-purple
#| classes: color-IBM-purple
#785EF0
```
```{markdown, eval=FALSE}
#| class-source: color-IBM-purple
#| classes: color-IBM-purple
rgb(120, 94, 240)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-IBM-magenta
#| classes: color-IBM-magenta
#DC267F
```
```{markdown, eval=FALSE}
#| class-source: color-IBM-magenta
#| classes: color-IBM-magenta
rgb(220, 38, 127)
```
:::

::::

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-IBM-orange
#| classes: color-IBM-orange
#| 
#FE6100
```

```{markdown, eval=FALSE}
#| class-source: color-IBM-orange
#| classes: color-IBM-orange
#| 
rgb(254, 97, 0)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-IBM-yellow
#| classes: color-IBM-yellow
#FFB000
```
```{markdown, eval=FALSE}
#| class-source: color-IBM-yellow
#| classes: color-IBM-yellow
rgb(255, 176, 0)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-gris
#| classes: color-gris
#949698
```
```{markdown, eval=FALSE}
#| class-source: color-gris
#| classes: color-gris
rgb(148, 150, 152)
```
:::

::::


```{r}
IBMBlue       <- "#648FFF"
IBMPurple     <- "#785EF0"
IBMMagenta    <- "#DC267F"
IBMOrange     <- "#FE6100"
IBMYellow     <- "#FFB000"
gris          <- "#949698"
```


```{tex, eval=FALSE}
\definecolor{IBMBlue}{HTML}{648FFF}
\definecolor{IBMPurple}{HTML}{785EF0}
\definecolor{IBMMagenta}{HTML}{DC267F}
\definecolor{IBMOrange}{HTML}{FE6100}
\definecolor{IBMYellow}{HTML}{FFB000}
\definecolor{gris}{HTML}{949698}
```


### Palette 4


```{css, echo=FALSE}
.color-bleuTOL {
  background-color: #332288;
}
.color-vertTOL {
  background-color: #117733;
}
.color-vertClairTOL {
  background-color: #44AA99;
}
.color-bleuClairTOL {
  background-color: #88CCEE;
}
.color-sableTOL {
  background-color: #DDCC77;
}
.color-parmeTOL {
  background-color: #CC6677;
}
.color-magentaTOL {
  background-color: #AA4499;
}
.color-roseTOL {
  background-color: #882255;
}
```


:::: {.columns}
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-bleuTOL
#| classes: color-bleuTOL
#| 
#332288
```
```{markdown, eval=FALSE}
#| class-source: color-bleuTOL
#| classes: color-bleuTOL
#| 
rgb(51, 34, 136)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-vertTOL
#| classes: color-vertTOL
#117733
```
```{markdown, eval=FALSE}
#| class-source: color-vertTOL
#| classes: color-vertTOL
rgb(17, 119, 51)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-vertClairTOL
#| classes: color-vertClairTOL
#44AA99
```
```{markdown, eval=FALSE}
#| class-source: color-vertClairTOL
#| classes: color-vertClairTOL
rgb(68, 170, 153)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-bleuClairTOL
#| classes: color-bleuClairTOL
#88CCEE
```
```{markdown, eval=FALSE}
#| class-source: color-bleuClairTOL
#| classes: color-bleuClairTOL
rgb(136, 204, 238)
```
:::
::::

:::: {.columns}
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-sableTOL
#| classes: color-sableTOL
#| 
#DDCC77
```
```{markdown, eval=FALSE}
#| class-source: color-sableTOL
#| classes: color-sableTOL
#| 
rgb(221, 204, 119)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-parmeTOL
#| classes: color-parmeTOL
#CC6677
```
```{markdown, eval=FALSE}
#| class-source: color-parmeTOL
#| classes: color-parmeTOL
rgb(204, 102, 119)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-magentaTOL
#| classes: color-magentaTOL
#AA4499
```
```{markdown, eval=FALSE}
#| class-source: color-magentaTOL
#| classes: color-magentaTOL
rgb(170, 68, 153)
```
:::
::: {.column width="25%"}
```{markdown, eval=FALSE}
#| class-source: color-roseTOL
#| classes: color-roseTOL
#882255
```
```{markdown, eval=FALSE}
#| class-source: color-roseTOL
#| classes: color-roseTOL
rgb(136, 34, 85)
```
:::
::::


```{r}
bleuTOL <- "#332288"
vertTOL <- "#117733"
vertClairTOL <- "#44AA99"
bleuClairTOL <- "#88CCEE"
sableTOL <- "#DDCC77"
parmeTOL <- "#CC6677"
magentaTOL <- "#AA4499"
roseTOL <- "#882255"
```


```{tex, eval=FALSE}
\definecolor{bleuTOL}{HTML}{332288}
\definecolor{vertTOL}{HTML}{117733}
\definecolor{vertClairTOL}{HTML}{44AA99}
\definecolor{bleuClairTOL}{HTML}{88CCEE}
\definecolor{sableTOL}{HTML}{DDCC77}
\definecolor{parmeTOL}{HTML}{CC6677}
\definecolor{magentaTOL}{HTML}{AA4499}
\definecolor{roseTOL}{HTML}{882255}
```




## Aix-Marseille University colors

### Oranges

```{css, echo=FALSE}
.color-orangeAMUClair {
  background-color: #FFA100;
}
.color-orangeAMUFonce {
  background-color: #FB4F14;
}
.color-jauneAMU {
  background-color: #EBB700;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-orangeAMUClair
#| classes: color-orangeAMUClair
#| 
#FFA100
```

```{markdown, eval=FALSE}
#| class-source: color-orangeAMUClair
#| classes: color-orangeAMUClair
#| 
rgb(255, 161, 0)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-orangeAMUFonce
#| classes: color-orangeAMUFonce
#FB4F14
```
```{markdown, eval=FALSE}
#| class-source: color-orangeAMUFonce
#| classes: color-orangeAMUFonce
rgb(251, 79, 20)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-jauneAMU
#| classes: color-jauneAMU
#EBB700
```
```{markdown, eval=FALSE}
#| class-source: color-jauneAMU
#| classes: color-jauneAMU
rgb(235, 183, 0)
```
:::

::::

```{r}
orangeAMUClair <- "#FFA100"
orangeAMUFonce <- "#FB4F14"
jauneAMU <- "#EBB700"
```


```{tex, eval=FALSE}
\definecolor{orangeAMUClair}{RGB}{255,161,20}
\definecolor{orangeAMUFonce}{RGB}{251,79,189}
\definecolor{jauneAMU}{RGB}{235,183,0}
```

### Rouges


```{css, echo=FALSE}
.color-rougeAMUClair {
  background-color: #CF2F44;
}
.color-rougeAMUMoyen {
  background-color: #96172E;
}
.color-bordeauAMU {
  background-color: #AA2F2F;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-rougeAMUClair
#| classes: color-rougeAMUClair
#| 
#CF2F44
```

```{markdown, eval=FALSE}
#| class-source: color-rougeAMUClair
#| classes: color-rougeAMUClair
#| 
rgb(207, 47, 68)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-rougeAMUMoyen
#| classes: color-rougeAMUMoyen
#96172E
```
```{markdown, eval=FALSE}
#| class-source: color-rougeAMUMoyen
#| classes: color-rougeAMUMoyen
rgb(150, 23, 46)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-bordeauAMU
#| classes: color-bordeauAMU
#AA2F2F
```
```{markdown, eval=FALSE}
#| class-source: color-bordeauAMU
#| classes: color-bordeauAMU
rgb(170, 47, 47)
```
:::

::::

```{r}
rougeAMUClair <- "#CF2F44"
rougeAMUMoyen <- "#96172E"
bordeauAMU <- "#AA2F2F"
```


```{tex, eval=FALSE}
\definecolor{rougeAMUClair}{RGB}{207,47,68}
\definecolor{rougeAMUMoyen}{RGB}{150,23,46}
\definecolor{bordeauAMU}{RGB}{170,47,47}
```

### Bleus

```{css, echo=FALSE}
.color-bleuAMUMoyen {
  background-color: #5482AB;
}
.color-bleuAMUFonce {
  background-color: #005A8B;
}
.color-bleuAMUClair {
  background-color: #00B0CA;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-bleuAMUMoyen
#| classes: color-bleuAMUMoyen
#| 
#5482AB
```

```{markdown, eval=FALSE}
#| class-source: color-bleuAMUMoyen
#| classes: color-bleuAMUMoyen
#| 
rgb(84, 130, 171)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-bleuAMUFonce
#| classes: color-bleuAMUFonce
#005A8B
```
```{markdown, eval=FALSE}
#| class-source: color-bleuAMUFonce
#| classes: color-bleuAMUFonce
rgb(0, 90, 139)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-bleuAMUClair
#| classes: color-bleuAMUClair
#00B0CA
```
```{markdown, eval=FALSE}
#| class-source: color-bleuAMUClair
#| classes: color-bleuAMUClair
rgb(0, 176, 202)
```
:::

::::

```{r}
bleuAMUMoyen <- "#5482AB"
bleuAMUFonce <- "#005A8B"
bleuAMUClair <- "#00B0CA"
```


```{tex, eval=FALSE}
\definecolor{bleuAMUMoyen}{RGB}{84,130,171}
\definecolor{bleuAMUFonce}{RGB}{0,90,139}
\definecolor{bleuAMUClair}{RGB}{0,176,202}
```

### Verts

```{css, echo=FALSE}
.color-vertAMUclair {
  background-color: #61C250;
}
.color-vertAMUPomme {
  background-color: #A5D867;
}
.color-vertAMUFonce {
  background-color: #00693C;
}
```

:::: {.columns}

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-vertAMUclair
#| classes: color-vertAMUclair
#| 
#61C250
```

```{markdown, eval=FALSE}
#| class-source: color-vertAMUclair
#| classes: color-vertAMUclair
#| 
rgb(97, 194, 80)
```

:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-vertAMUPomme
#| classes: color-vertAMUPomme
#A5D867
```
```{markdown, eval=FALSE}
#| class-source: color-vertAMUPomme
#| classes: color-vertAMUPomme
rgb(165, 216, 103)
```
:::

::: {.column width="33%"}
```{markdown, eval=FALSE}
#| class-source: color-vertAMUFonce
#| classes: color-vertAMUFonce
#00693C
```
```{markdown, eval=FALSE}
#| class-source: color-vertAMUFonce
#| classes: color-vertAMUFonce
rgb(0, 105, 60)
```
:::

::::



```{r}
vertAMUclair <- "#61C250"
vertAMUPomme <- "#A5D867"
vertAMUFonce <- "#00693C"
```

```{tex, eval=FALSE}
\definecolor{vertAMUclair}{RGB}{97,194,80}
\definecolor{vertAMUPomme}{RGB}{165,216,103}
\definecolor{vertAMUFonce}{RGB}{0,105,60}
```


