# Insert emojis

\[May 2023\]

The other day, [Bertille](bertillepicard.github.io/) told me she had troubles with Quarto and Emojis: the latter did not appear in the PDF documents. I thought it was pretty simple and I did not remember struggling with that. I should have guessed, however, if that Bertille was having an issue, it was not not on something trivial. The former solution that was working (or at least I believe so) with R markdown does not work with quarto...

An issue was opened on quarto-dev: <https://github.com/quarto-dev/quarto-cli/issues/4492>, but the [answer given by Susan VanderPlas unfortunately](https://github.com/quarto-dev/quarto-cli/issues/4492#issuecomment-1548655951) does not work on my computer. This is my workaround this issue.

1.  In the YAML, insert the following, to support the emojis in the PDF:

    ```{yaml}
    pdf:
     documentclass: scrreprt
     pdf-engine: lualatex
     include-in-header:
     - text: |
         \usepackage{emoji}
    ```

    This loads the [{emoji}](https://ctan.math.washington.edu/tex-archive/macros/luatex/latex/emoji/emoji-doc.pdf) LaTeX package and as the latter requires lualatex as the pdf engine, we set the pdf engine to LuaLaTeX.

2.  To make the emojis also available on the HTML file, we also need to add the following instruction in the YAML:

    ```{yaml}
    from: markdown+emoji
    ```

3.  In each `qmd` file where we need to include emojis, we can define:

    - a tibble that contains the unicode runes corresponding to the different skin tones (5 of them)
    - a tibble with the names of the emojis and the corresponding runes, from the [{emo(ji)}](https://github.com/hadley/emo) package
    - a function that maps a name to the unicode runes and returns the emoji either for LaTeX output or HTML output.
    - Note that some emojis are not in {emo(ji)} (e.g.: `weary`). For those, we use the standard way of writing in quarto.

    ```{r}
    modifier_sequence_tones <- 
      tibble::tribble(
        ~code_point, ~tone,
        "1F3FB", "_light_skin_tone",
        "1F3FC", "_medium_light_skin_tone",
        "1F3FD", "_medium_skin_tone",
        "1F3FE", "_medium_dark_skin_tone",
        "1F3FF", "_dark_skin_tone"
      )
    emojis_all <- 
      emo::jis |>
      dplyr::mutate(alias = stringr::str_replace_all(name, " ", "_"),
                    alias = stringr::str_replace_all(alias, "-", "_"),
                    alias = stringr::str_remove_all(alias, ":"))
    
    emoji <- function(x) {
      if(length(x) != 1)  
          stop("Error: the length of x is not equal to 1.")
      if (knitr::is_latex_output()) {
        resul <- stringr::str_c("\\emoji{", stringr::str_replace_all(x, "_", "-"), "}")
      } else if (knitr::is_html_output()) {
        ind_match <- match(x, emojis_all$alias)
        runes_match <- emojis_all$runes[ind_match]
        if (!is.na(ind_match)) {
          resul <- 
            stringr::str_split(runes_match, " ") |>
            purrr::map(~as.integer(as.hexmode(.))) |>
            purrr::map(~intToUtf8(.)) |>
            unlist()
        } else {
          resul <- stringr::str_c(":", x, ":")
        }
      } else {
        resul <- x
      }
      resul
    }
    ```

4.  In the `qmd` file, to insert an emoji, we need to know its name or alias as defined in the [{emoji} package documentation](https://ctan.math.washington.edu/tex-archive/macros/luatex/latex/emoji/emoji-doc.pdf).

    ```{markdown}
    `r emoji("weary")`
    `r emoji("blue_heart")`
    ```

`r emoji("weary")`
`r emoji("blue_heart")`


## Skin tones

To use different skin tones, whenever the emoji allows for it, we just need to append one of the following suffixes to the name of the emoji:

- `"_light_skin_tone"`{.R}: light skin
- `"_medium_light_skin_tone"`{.R}: medium light skin
- `"_medium_skin_tone"`{.R}:  medium skin
- `"_medium_dark_skin_tone"`{.R}: medium dark skin
- `"_dark_skin_tone`{.R}: dark skin

```{markdown}
`r emoji("waving_hand")`
`r emoji("waving_hand_light_skin_tone")`
`r emoji("waving_hand_medium_light_skin_tone")`
`r emoji("waving_hand_medium_skin_tone")`
`r emoji("waving_hand_medium_dark_skin_tone")`
`r emoji("waving_hand_dark_skin_tone")`
```

`r emoji("waving_hand")`
`r emoji("waving_hand_light_skin_tone")`
`r emoji("waving_hand_medium_light_skin_tone")`
`r emoji("waving_hand_medium_skin_tone")`
`r emoji("waving_hand_medium_dark_skin_tone")`
`r emoji("waving_hand_dark_skin_tone")`

## List of all the available emojis

Let us list all the emojis using the work done by Xiangdong Zeng: <https://github.com/stone-zeng/latex-emoji>

```{r}
# download.file(
# "https://raw.githubusercontent.com/stone-zeng/latex-emoji/main/data/emoji.json", 
# destfile = "data/emoji.json")
emojis <- jsonlite::fromJSON("data/emoji.json")
```

```{r, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
#| tbl-cap: List of emojis
#| label: emojis-latex
library(tidyverse)
emojis %>% 
  unnest(aliases) %>% 
  select(emoji, alias = aliases, description, category, tags, skin_tones) %>% 
  rowwise() %>% 
  mutate(r_emoji = emoji(alias)) %>% 
  knitr::kable()
```
